A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-31 paper.tex
Add future work in paper organization

\subsection{Paper Organization}
The rest of this paper is organized as follows. In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed. In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture is illustrated. In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices. In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained. The analysis results are given in Section~\ref{section:evaluation}. Finally, we conclude the paper in Section~\ref{section:conclusion}.

@@

\section{Future Work}
In the subscription-based data trading, there are some issues that worth discussing and improving. Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation. Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers. Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures. However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.

>>>>

\subsection{Paper Organization}
The rest of this paper is organized as follows. In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed. In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture is illustrated. In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices. In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained. The analysis results are given in Section~\ref{section:evaluation}. Finally, we conclude the paper in Section~\ref{section:conclusion} and the future work in Section~\ref{section:future_work}.

@@

\section{Future Work}
\label{section:future_work}
In the subscription-based data trading, there are some issues that worth discussing and improving. Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation. Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers. Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures. However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
